\section{Analysis of Incompleteness}
\subsection*{Poorly Connected Instance Nodes}
This query finds instance nodes with one or zero semantic relationships (i.e., relationships other than IS\_A or FROM), which may indicate concepts that are mentioned but not well-integrated.

\begin{longtable}{p{0.45\textwidth} p{0.45\textwidth}}
\toprule
\textbf{Entity} & \textbf{NumberOfDanglingNodes} \\
\midrule
\endfirsthead
\endhead
Authority & 9 \\
Exhibit A & 9 \\
Owner & 7 \\
Conewago Township & 6 \\
Sewer System & 6 \\
York County Prison & 6 \\
Authority Engineer & 5 \\
Contractor & 5 \\
Lateral & 5 \\
Magisterial District Judge & 5 \\
Sanitary Sewer System & 5 \\
Building Sewer & 4 \\
Conewago Township Sewer Authority & 4 \\
Connection Permit & 4 \\
EDU & 4 \\
Exhibit "A" & 4 \\
Pennsylvania & 4 \\
Res. No. 1993-4 & 4 \\
Service Lateral & 4 \\
The Authority & 4 \\
Township & 4 \\
Vice Chairman & 4 \\
Assistant Secretary & 3 \\
Authority's Engineer & 3 \\
Authority's Inspector & 3 \\
Chairman & 3 \\
Chapter 150 & 3 \\
Engineer & 3 \\
Escrow & 3 \\
Manhole & 3 \\
Record Drawings & 3 \\
Sewage Treatment Plant & 3 \\
Solicitor & 3 \\
This Chapter & 3 \\
§ 115-7 & 3 \\
§ 150-2 & 3 \\
§ 150-38 & 3 \\
15 Pa.C.S.A. § 1322 (Pocket Part 1986) & 2 \\
53 Pa.C.S.A. § 5601 et seq. & 2 \\
AASHTO No. 8 & 2 \\
AASHTO No. 8 Coarse Aggregate & 2 \\
Accountant & 2 \\
Act 428 Of 1968 & 2 \\
Act Of July 20, 1968, P.L. 459, No. 216, 15 Pa.C.S.A. § 1322 (Pocket Part 1986) & 2 \\
Applicant & 2 \\
Application & 2 \\
Articles Of Incorporation & 2 \\
Bennett Run Project & 2 \\
Billing Clerk & 2 \\
Biochemical Oxygen Demand (BOD) & 2 \\
Bond Counsel & 2 \\
Bylaws & 2 \\
Chapter 150, Sewer Rules And Regulations & 2 \\
Conewago Code & 2 \\
Conewago Township Sewer System & 2 \\
Construction Manager & 2 \\
Court & 2 \\
DEP & 2 \\
Dam Safety And Waterway Management & 2 \\
Declaration Of Taking & 2 \\
Deeds Of Dedication & 2 \\
District Justice & 2 \\
Dover Treatment Plant & 2 \\
Dwelling Unit & 2 \\
Easement & 2 \\
Employee & 2 \\
Equivalent Dwelling Unit & 2 \\
Exhibit "C" & 2 \\
Exhibit A23 & 2 \\
Grinder Stations & 2 \\
Industrial Waste Discharge Permit & 2 \\
Inspection Escrow & 2 \\
Lateral Connection & 2 \\
Pennsylvania Infrastructure Investment Authority & 2 \\
Permit & 2 \\
Permits & 2 \\
Person & 2 \\
Property Owner & 2 \\
Property Plats & 2 \\
Qualified Person & 2 \\
Recording Secretary & 2 \\
Remedial Program & 2 \\
Res. No. 1993-3 & 2 \\
Res. No. 2009-1 & 2 \\
Res. No. 2020-2 & 2 \\
Res. No. 2022-1 & 2 \\
Reserve Capacity Agreement & 2 \\
Resident Inspector & 2 \\
Resolution & 2 \\
School District & 2 \\
Secretary & 2 \\
Service Connection & 2 \\
Sewage Treatment System & 2 \\
Sewer Lateral & 2 \\
Sewer Main & 2 \\
Subsection B(5)(g)[1][a] & 2 \\
Tapping Fee & 2 \\
Township Plumbing Code & 2 \\
Warranty Period & 2 \\
Wastewater System & 2 \\
Wetlands & 2 \\
Written Warning & 2 \\
Y-Fitting & 2 \\
§ 115-2 & 2 \\
§ 115-3 & 2 \\
§ 121-2 & 2 \\
§ 126-1 & 2 \\
§ 132-10 & 2 \\
§ 132-11 & 2 \\
§ 132-5 & 2 \\
§ 132-6 & 2 \\
§ 150-16 & 2 \\
§ 150-17 & 2 \\
§ 150-20 & 2 \\
§ 150-22 & 2 \\
§ 150-27 & 2 \\
§ 150-3 & 2 \\
§ 150-30 & 2 \\
§ 150-37 & 2 \\
§ 150-43 & 2 \\
§ 162-1 & 2 \\
§ 162-2 & 2 \\
§ 175-1 & 2 \\
§ 175-12 & 2 \\
§ 175-16 & 2 \\
§ 175-9 & 2 \\
§ 188-3 & 2 \\
§ 71-1 & 2 \\
§ 71-3 & 2 \\
§ 71-4 & 2 \\
§ 99-1 & 2 \\
\$1,500 & 1 \\
10-25-2022 & 1 \\
1990 Promissory Note & 1 \\
2-23-2010 & 1 \\
2002 Promissory Note & 1 \\
33 U.S.C. § 1344 & 1 \\
404 Permit & 1 \\
53 P.S. § 10101 Et Seq. & 1 \\
53 Pa.C.S.A § 1381 Et Seq. & 1 \\
53 Pa.C.S.A. § 5601 Et Seq. & 1 \\
65 Pa.C.S.A. § 701 Et Seq. & 1 \\
ASTM 74 & 1 \\
Act 203 & 1 \\
Act 203 Of 1990 Legislation & 1 \\
Act 537 Sewerage Facilities Plan & 1 \\
Action In Assumpsit & 1 \\
Administrative Fee & 1 \\
Alley & 1 \\
Annual Charge For Allocated Capacity & 1 \\
Annual Reservation Fee & 1 \\
Apparatus & 1 \\
Appendix A210 & 1 \\
Appendix A230 & 1 \\
Applicant's Contractor & 1 \\
Applicant's System & 1 \\
April 15, 2000 & 1 \\
April 30, 1993 & 1 \\
Article I & 1 \\
Article III & 1 \\
Article IV & 1 \\
Assistant Treasurer & 1 \\
Attorney's Fees & 1 \\
Auditor & 1 \\
August 1, 1993 & 1 \\
Authority Facilities & 1 \\
Authority Member & 1 \\
Authority's \$600,000 Guaranteed Sewer Project Note - Series of 2000 & 1 \\
Authority's Procedures & 1 \\
Authority's Representative & 1 \\
Authority's Representatives & 1 \\
Authority's Rules And Regulations & 1 \\
Authority's Technical Specifications Covering Sanitary Sewers Installed By Developers & 1 \\
Bank Account & 1 \\
Bank Statements & 1 \\
Billing And Accounts Payable Records & 1 \\
Blasting Bonds & 1 \\
Board & 1 \\
Board Member & 1 \\
Board of the Authority & 1 \\
Building Sewers & 1 \\
CTSA & 1 \\
CTSA Engineer & 1 \\
CTSA Sewage Treatment Facility & 1 \\
CTSA Staff & 1 \\
Car Wash & 1 \\
Certificate Of Satisfactory Construction & 1 \\
Cesspool & 1 \\
Chapter 162 & 1 \\
Chapter 175 & 1 \\
Chapter 94 Report & 1 \\
Checklist For Development Plans & 1 \\
Civil Action & 1 \\
Cleanouts & 1 \\
Commonwealth of Pennsylvania & 1 \\
Commonwealth-Chartered Lending Institution & 1 \\
Complainant & 1 \\
Complaint & 1 \\
Condemnee & 1 \\
Conewago Township Ordinances & 1 \\
Conewago Township Sewer Authority Board & 1 \\
Conewago Township Sewer Authority's Resolution 1992-2 & 1 \\
Conewego Code & 1 \\
Connection And Tapping Fees & 1 \\
Connection Charge & 1 \\
Construction Escrow Agreement & 1 \\
Construction Plans & 1 \\
Consulting Engineer & 1 \\
County Soil Survey & 1 \\
Court Costs & 1 \\
Ctsa & 1 \\
Curbline & 1 \\
Dep & 1 \\
Department of Environmental Protection Municipal Wasteload Management Regulations & 1 \\
Developer & 1 \\
Double Bend & 1 \\
Dover Township Wastewater Treatment Plant & 1 \\
Eminent Domain Proceeding & 1 \\
Employee Insurance Records & 1 \\
Employee Of The Authority & 1 \\
Employment Decision & 1 \\
Equivalent Dwelling Unit (EDU) & 1 \\
Escrow Account & 1 \\
Escrow Deposit & 1 \\
Escrow Records & 1 \\
Executive Review & 1 \\
Exhibit & 1 \\
Exhibit "B" & 1 \\
Exhibit A, Application To Construct Sewerage Facilities & 1 \\
Exhibit A, Landlord Responsibility Acknowledgement Form & 1 \\
Exhibit A.8 & 1 \\
Exhibit A21 & 1 \\
Exhibit C & 1 \\
Exhibit24 & 1 \\
F-T, LLLP & 1 \\
Feasibility Study & 1 \\
February 1, 1996 & 1 \\
Federal Occupational Safety And Health Administration & 1 \\
Federal Occupational Safety And Health Administration Regulations & 1 \\
Federally-Chartered Lending Institution & 1 \\
Fernco™ & 1 \\
Ferrule & 1 \\
Final Plans & 1 \\
Final Subdivision Plans & 1 \\
Financial Records & 1 \\
Financial Security & 1 \\
Fresh Air Vent & 1 \\
Fueling Facility & 1 \\
Garage & 1 \\
Governing Body Of The Municipality & 1 \\
Gravity Sewer System & 1 \\
Grease Interceptor Detail & 1 \\
Grease Trap & 1 \\
Grinder Pump Basin & 1 \\
Highway Occupancy Permit & 1 \\
Improved Property & 1 \\
Independent Counsel For The Authority & 1 \\
Industrial Waste Discharge Agreement & 1 \\
Industrial Wastes & 1 \\
Infiltration And Detection & 1 \\
Inspection Fee & 1 \\
Inspector & 1 \\
Installation Cost & 1 \\
Interceptor & 1 \\
Investment Advisor & 1 \\
Irrevocable Letters Of Credit & 1 \\
July 1, 2005 & 1 \\
July 31, 1993 & 1 \\
Lane & 1 \\
Leaks & 1 \\
Legal Descriptions & 1 \\
Lending Institution & 1 \\
Letter Of Approval & 1 \\
Letter Report & 1 \\
List Of Contractors & 1 \\
List Of Material Suppliers & 1 \\
List Of Subcontractors & 1 \\
Loan Agreement & 1 \\
Magnetic Polyethylene Tape & 1 \\
Manhole Inspection & 1 \\
Manual Of The Conewago Township Sewer Authority & 1 \\
March 28, 2019 & 1 \\
Material Compliance Certifications & 1 \\
Material Samples & 1 \\
May 1, 1993 & 1 \\
Monthly Billing Calculation & 1 \\
Municipal Claim Or Lien & 1 \\
Municipal Lien & 1 \\
Municipal Permits & 1 \\
Municipal Records Manual & 1 \\
Mushroom Vent & 1 \\
NPDES Permit & 1 \\
National Wetland Inventory Map & 1 \\
Natural Resources Conservation Service & 1 \\
Offices Of The Conewago Township Sewer Authority & 1 \\
Oil Interceptor Detail & 1 \\
Oil Separator & 1 \\
Original Resolution & 1 \\
PENNVEST & 1 \\
PLGIT Records & 1 \\
Partial Release Estimate & 1 \\
Pennsylvania Dep & 1 \\
Pennsylvania Department Of Environmental Protection & 1 \\
Pennsylvania Department Of Transportation & 1 \\
Pennsylvania Department Of Transportation Regulations & 1 \\
Pennsylvania Law & 1 \\
Pennsylvania Municipal Records Act & 1 \\
Pennsylvania Municipalities Authorities Act & 1 \\
Pennsylvania's Sunshine Act & 1 \\
Pennvest Records & 1 \\
Permanent Flow Meter & 1 \\
Permit And Inspection Fees & 1 \\
Permit(s) & 1 \\
Pipe Trench & 1 \\
Policy & 1 \\
Portable Flow Meter & 1 \\
Preconstruction Meeting & 1 \\
Preliminary Plan & 1 \\
Preliminary Plans & 1 \\
Privy Vault & 1 \\
Procedure & 1 \\
Project & 1 \\
Project Estimate & 1 \\
Property & 1 \\
Proposed Project & 1 \\
Public Sewer & 1 \\
Public Square & 1 \\
Punch List Items & 1 \\
Qualified Professional & 1 \\
Reimbursement Agreement & 1 \\
Res. No. 1991-1 & 1 \\
Res. No. 1991-2 & 1 \\
Res. No. 1993-1 & 1 \\
Res. No. 1993-2 & 1 \\
Res. No. 1993-6 & 1 \\
Res. No. 1998-3 & 1 \\
Res. No. 1999-1 & 1 \\
Res. No. 2000-1 & 1 \\
Res. No. 2002-2 & 1 \\
Res. No. 2004-1 & 1 \\
Res. No. 2004-2 & 1 \\
Res. No. 2005-1 & 1 \\
Res. No. 2007-2 & 1 \\
Res. No. 2010-1 & 1 \\
Res. No. 2016-1 & 1 \\
Res. No. 2017-2 & 1 \\
Res. No. 2020-1 & 1 \\
Res. No. 2023-1 & 1 \\
Res. No. 2024-1 & 1 \\
Reserve Capacity Charges & 1 \\
Reserve Capacity Fee & 1 \\
Resolution No. 1992-1 & 1 \\
Resolutions & 1 \\
Restrictive Account & 1 \\
Right-Of-Way Agreement & 1 \\
Rights-Of-Way & 1 \\
Riser & 1 \\
Road & 1 \\
Road Right-Of-Way & 1 \\
School Building & 1 \\
School Property & 1 \\
Screw-Type Ferrule & 1 \\
Seal Of The Authority & 1 \\
Secretary-Treasurer & 1 \\
Section 1 & 1 \\
Section 150-29 & 1 \\
Separator & 1 \\
Septic Tank & 1 \\
Sewage Connection Permit & 1 \\
Sewage Treatment & 1 \\
Sewer & 1 \\
Sewer Extension Agreement & 1 \\
Sewer Extension Reimbursement Agreement & 1 \\
Sewer Right-Of-Way & 1 \\
Sewer Right-Of-Way Line & 1 \\
Sewer Rules And Regulations & 1 \\
Sewerage Facilities & 1 \\
Sewerage Project & 1 \\
Sexual Harassment Policy & 1 \\
Sinkhole & 1 \\
Sketch Plan & 1 \\
Sludge Contract Records & 1 \\
State Route 0921 & 1 \\
Stephen P. Linebaugh & 1 \\
Subsection D & 1 \\
Subsequent Amendments & 1 \\
Surfactant & 1 \\
Tapping Agreement & 1 \\
Technical Specifications Covering Sanitary Sewers Installed By Developers & 1 \\
Termination & 1 \\
The Act & 1 \\
The Township & 1 \\
Township Road Occupancy Regulations & 1 \\
Trap & 1 \\
Treasurer & 1 \\
Trench & 1 \\
U.S. Fish And Wildlife Service & 1 \\
Vacant Lot Sewer Reservation Agreement & 1 \\
Vehicle Repair Facility & 1 \\
Video Inspection & 1 \\
Violator & 1 \\
Waiver Of Liens & 1 \\
Warranty Phase & 1 \\
Water Company & 1 \\
Water Meter & 1 \\
Water Obstruction Permit & 1 \\
Water Quality Management Permit & 1 \\
Water Quality Management Permit Application & 1 \\
Water Shutoff & 1 \\
Y-Connection & 1 \\
York Concrete Products & 1 \\
York County & 1 \\
York Water Company & 1 \\
§ 115-1 & 1 \\
§ 115-4 & 1 \\
§ 115-5 & 1 \\
§ 115-6 & 1 \\
§ 115-8 & 1 \\
§ 121-3 & 1 \\
§ 121-4 & 1 \\
§ 132-1 & 1 \\
§ 132-2 & 1 \\
§ 132-3 & 1 \\
§ 132-4 & 1 \\
§ 132-7 & 1 \\
§ 132-8 & 1 \\
§ 132-9 & 1 \\
§ 144-1 & 1 \\
§ 144-2 & 1 \\
§ 144-3 & 1 \\
§ 150-1 & 1 \\
§ 150-10 & 1 \\
§ 150-12 & 1 \\
§ 150-13 & 1 \\
§ 150-14 & 1 \\
§ 150-15 & 1 \\
§ 150-18 & 1 \\
§ 150-23 & 1 \\
§ 150-24 & 1 \\
§ 150-25 & 1 \\
§ 150-26 & 1 \\
§ 150-28 & 1 \\
§ 150-29 & 1 \\
§ 150-32 & 1 \\
§ 150-33 & 1 \\
§ 150-34 & 1 \\
§ 150-36 & 1 \\
§ 150-4 & 1 \\
§ 150-40 & 1 \\
§ 150-41 & 1 \\
§ 150-42 & 1 \\
§ 150-5 & 1 \\
§ 150-6 & 1 \\
§ 150-7 & 1 \\
§ 150-8 & 1 \\
§ 175-10 & 1 \\
§ 175-11 & 1 \\
§ 175-13 & 1 \\
§ 175-15 & 1 \\
§ 175-2 & 1 \\
§ 188-1 & 1 \\
§ 188-2 & 1 \\
§ 188-4 & 1 \\
§ 20-5 & 1 \\
§ 34-5 & 1 \\
§ 46-10 & 1 \\
§ 46-8 & 1 \\
§ 71-2 & 1 \\
§ 71-5 & 1 \\
§ 82-3 & 1 \\
§ 82-4 & 1 \\
§ 99-3 & 1 \\
§ 99-4 & 1 \\
§ DL-1 & 1 \\
\bottomrule
\end{longtable}
\subsubsection*{Interpretation}
A value of 1 means there is a single, unique entity with this name that is poorly connected. A value greater than 1 indicates multiple, unmerged instances of the same conceptual entity, all of which are poorly connected, highlighting both incompleteness and potential inconsistency.
\clearpage
\subsection*{Regulations Missing 'APPLIES\_TO' Relationship}
This query identifies 'Regulation' instances that are not linked to anything via an 'APPLIES\_TO' relationship, suggesting an incomplete definition.

\begin{longtable}{p{0.45\textwidth} p{0.45\textwidth}}
\toprule
\textbf{Concept} & \textbf{Occurrences} \\
\midrule
\endfirsthead
\endhead
Chapter 105 & 2 \\
Chapter 150, Sewer Rules And Regulations & 2 \\
Rules And Regulations & 2 \\
Sewer Rules And Regulations & 2 \\
Dam Safety And Waterway Management & 1 \\
Department of Environmental Protection Municipal Wasteload Management Regulations & 1 \\
Federal Occupational Safety And Health Administration Regulations & 1 \\
Pennsylvania Department Of Transportation Regulations & 1 \\
Township Road Occupancy Regulations & 1 \\
§ 60-1 & 1 \\
\bottomrule
\end{longtable}
\subsubsection*{Interpretation}
The 'Occurrences' column shows how many times a specific, incompletely defined concept appears. A high number for a particular concept signals a recurring issue of ambiguity or incompleteness in the source document.
\clearpage
\section{Analysis of Inconsistency}
\subsection*{Ambiguous Terms (Inconsistent Types)}
This query finds terms that have been assigned multiple different types, indicating ambiguity in the source text or extraction errors.

\begin{longtable}{p{0.3\textwidth} p{0.3\textwidth} p{0.3\textwidth}}
\toprule
\textbf{AmbiguousEntity} & \textbf{Occurrences} & \textbf{Types} \\
\midrule
\endfirsthead
\endhead
Conewago Township Sewer Authority & 30 & Organization, GovernmentAuthority, GoverningBody, Government Authority, Government Agency, Authority \\
Authority & 22 & Organization, Board, Term, GovernmentAuthority, GoverningBody, Party \\
Conewago Township & 12 & Municipality, Township, Jurisdiction \\
Building Sewer & 10 & InfrastructureComponent, Pipe, Term, BuildingSewer \\
Exhibit A & 10 & LegalDocument, Exhibit \\
Sewer System & 9 & InfrastructureComponent, Component, System, Infrastructure \\
The Authority & 8 & Organization, GoverningBody \\
Conewago Township Sewer System & 7 & InfrastructureComponent, System, Sewer System, Infrastructure, UtilitySystem \\
Lateral & 7 & InfrastructureComponent, Sewer Component, Pipe, Term, Component, Lateral \\
Owner & 7 & Person, Term \\
Improved Property & 6 & Term, Property \\
Pennsylvania & 6 & State, GoverningBody \\
Township & 6 & Municipality, Jurisdiction \\
York County Prison & 6 & Prison, Facility \\
Authority Engineer & 5 & Person, Role, Engineer \\
Developer & 5 & Person, Role, Party, Position \\
Escrow & 5 & FinancialAccount, FinancialInstrument \\
Magisterial District Judge & 5 & Judge, Official, JudicialOfficer \\
Sanitary Sewer System & 5 & InfrastructureComponent, System, Infrastructure \\
Applicant & 4 & Person, Role \\
Authority's Inspector & 4 & Person, Inspector \\
Business Corporations Law & 4 & Statute, Law \\
CTSA & 4 & Organization, Board, GoverningBody, Authority \\
Conewago Township Sewer Authority Board & 4 & Organization, Board, GovernmentAuthority \\
Engineer & 4 & Person, Official, Position \\
Financial Security & 4 & FinancialInstrument, Security \\
Pennsylvania Department Of Environmental Protection & 4 & Organization, GoverningBody \\
Service Lateral & 4 & InfrastructureComponent, Pipe \\
Sewer & 4 & InfrastructureComponent, Pipe, Sewer \\
Solicitor & 4 & Person, Official, Position \\
Vice Chairman & 4 & Role, Officer, Position \\
Assistant Secretary & 3 & Officer, Position \\
Chairman & 3 & Official, Role, Officer \\
Declaration Of Taking & 3 & LegalFiling, Legal Document \\
Easement & 3 & PropertyRight, Property Right \\
Equivalent Dwelling Unit & 3 & Unit, UnitOfMeasurement \\
Manhole & 3 & InfrastructureComponent, Infrastructure \\
Pennsylvania Infrastructure Investment Authority & 3 & Organization, GovernmentAuthority, GoverningBody \\
Permit & 3 & Permit, LegalDocument \\
Record Drawings & 3 & Specifications, Drawing, LegalDocument \\
Resolution & 3 & Resolution, Document \\
Sewage Treatment Plant & 3 & InfrastructureComponent, Facility, Plant \\
Sewer Rules And Regulations & 3 & Regulation, Law \\
This Chapter & 3 & Chapter, LegalDocument, DocumentSection \\
53 Pa.C.S.A. § 5601 et seq. & 2 & Statute, DocumentSection \\
AASHTO No. 8 & 2 & MaterialStandard, Material \\
Accountant & 2 & Person, Position \\
Act Of July 20, 1968, P.L. 459, No. 216, 15 Pa.C.S.A. § 1322 (Pocket Part 1986) & 2 & Statute, DocumentSection \\
Applicant's Contractor & 2 & Person, Contractor \\
Application & 2 & LegalDocument, Application \\
Article I & 2 & Chapter, DocumentArticle \\
Auditor & 2 & Official, Advisor \\
Billing Clerk & 2 & Person, Official \\
Biochemical Oxygen Demand (BOD) & 2 & UnitOfMeasurement, ChemicalProperty \\
Bond Counsel & 2 & Position, Advisor \\
Bylaws & 2 & LegalDocument, Law \\
CTSA Staff & 2 & GoverningBody, Position \\
Chapter 175 & 2 & Chapter, DocumentChapter \\
Conewago Township Sewer Authority Rules And Regulations & 2 & Manual, LegalDocument \\
Consulting Engineer & 2 & Engineer, Position \\
Court & 2 & Roadway, Court \\
Dam Safety And Waterway Management & 2 & Regulation, RegulationTitle \\
Deeds Of Dedication & 2 & LegalDocument, Deed \\
District Justice & 2 & Judge, Position \\
Dover Treatment Plant & 2 & Facility, Treatment Plant \\
Dwelling Unit & 2 & UnitOfMeasurement, DwellingUnit \\
Employee & 2 & Person, Position \\
Final Plans & 2 & LegalDocument, Plan \\
Industrial Wastes & 2 & Waste, Term \\
Inspection Escrow & 2 & FinancialAccount, FinancialInstrument \\
Investment Advisor & 2 & Role, Advisor \\
Lateral Connection & 2 & Connection, Infrastructure \\
Manual Of The Conewago Township Sewer Authority & 2 & Manual, LegalDocument \\
Municipality & 2 & Municipality, GoverningBody \\
PENNVEST & 2 & Organization, GovernmentAuthority \\
Pennsylvania Department Of Transportation & 2 & GoverningBody, GovernmentAgency \\
Permits & 2 & Permit, Record \\
Person & 2 & Term, Entity \\
Preliminary Plans & 2 & LegalDocument, Plan \\
Property Plats & 2 & LegalDocument, Plat \\
Recording Secretary & 2 & Official, Position \\
Riser & 2 & InfrastructureComponent, Component \\
School District & 2 & Organization, District \\
Secretary & 2 & Officer, Position \\
Service Connection & 2 & Sewer Component, ServiceConnection \\
Sewage Treatment System & 2 & Facility, System \\
Sewer Authority & 2 & GoverningBody, Government Agency \\
Sewer Authority Solicitor & 2 & Official, Advisor \\
Sewer Lateral & 2 & InfrastructureComponent, Pipe \\
Sewer Main & 2 & InfrastructureComponent, Pipe \\
Sewerage Facilities & 2 & Facility, Infrastructure \\
Township Plumbing Code & 2 & LegalDocument, Code \\
Trap & 2 & InfrastructureComponent, Component \\
Warning Tape & 2 & InfrastructureComponent, Component \\
Water Quality Management Permit Application & 2 & Application, Permit Application \\
Y-Fitting & 2 & InfrastructureComponent, Fitting \\
§ 20-6 & 2 & Law, Code \\
§ 20-9 & 2 & DocumentSection, Law \\
§ 46-3 & 2 & Chapter, DocumentSection \\
§ 46-4 & 2 & Statute, DocumentSection \\
\bottomrule
\end{longtable}
\subsubsection*{Interpretation}
The results show terms creating ambiguity. 'Occurrences' is the number of separate nodes sharing this name with different types. 'Types' lists the different classifications assigned.
\clearpage
\subsection*{Circular Type Dependencies}
This query identifies logical loops in the type hierarchy (e.g., A IS\_A B, B IS\_A A), which represent a structural inconsistency in the ontology.

\begin{longtable}{p{0.45\textwidth} p{0.45\textwidth}}
\toprule
\textbf{CircularPath} & \textbf{Occurrences} \\
\midrule
\endfirsthead
\endhead
Board, GoverningBody, Official, Person, Position & 1500 \\
Board, Official, Person, Position & 76 \\
Board, GoverningBody, Official, Person & 22 \\
Board, GoverningBody, Official, Position & 22 \\
Board, GoverningBody, Person, Position & 17 \\
GoverningBody, Official, Person, Position & 17 \\
Board, GoverningBody, Official & 9 \\
Board, Person, Position & 7 \\
Official, Person, Position & 7 \\
Board, GoverningBody & 5 \\
Law, LegalDocument & 5 \\
GoverningBody, Official, Person & 4 \\
GoverningBody, Official, Position & 4 \\
Chapter, DocumentSection & 2 \\
GoverningBody, Official & 2 \\
Official, Person & 2 \\
Official, Position & 2 \\
\bottomrule
\end{longtable}
\subsubsection*{Interpretation}
Any result from this query represents a significant logical inconsistency in the inferred ontology. 'CircularPath' shows the nodes forming the definitional loop.
\clearpage
\subsection*{Most Unstable Concepts (High Refinement)}
This query identifies concepts that required the most refinement cycles (merging, re-typing), indicating they were the most ambiguous or inconsistently represented in the source text.

\begin{longtable}{p{0.3\textwidth} p{0.3\textwidth} p{0.3\textwidth}}
\toprule
\textbf{Entity} & \textbf{Occurrences} & \textbf{MaxModifications} \\
\midrule
\endfirsthead
\endhead
Chapter 20 & 1 & 10 \\
Municipalities Planning Code & 1 & 9 \\
Article I & 1 & 7 \\
§ 46-2 & 2 & 6 \\
Sewer Authority & 2 & 5 \\
CTSA & 1 & 5 \\
Authority & 8 & 4 \\
CTSA Solicitor & 1 & 4 \\
Sewer Authority Solicitor & 1 & 4 \\
Subdivision And Land Development Plan & 1 & 4 \\
§ 46-3 & 2 & 3 \\
§ 20-6 & 2 & 3 \\
§ 20-9 & 2 & 3 \\
§ 46-4 & 2 & 3 \\
Investment Advisor & 2 & 3 \\
Municipality & 1 & 3 \\
§ 46-1 & 1 & 3 \\
§ 20-1 & 1 & 3 \\
Official Of The Authority & 1 & 3 \\
Res. No. 2021-1 & 1 & 3 \\
CTSA - Base - Remove.docx & 1 & 3 \\
§ 1-1 & 1 & 3 \\
§ 20-7 & 1 & 3 \\
§ 20-4 & 1 & 3 \\
§ 34-4 & 1 & 3 \\
\bottomrule
\end{longtable}
\subsubsection*{Interpretation}
'Occurrences' is the number of nodes with this name that needed modification. 'MaxModifications' is the highest refinement count for any single node of that name, a direct measure of instability.
\clearpage